Summarize twas: chr17 to 22

### 2020-09-14 analysis/index.Rmd
susieI plots

# Test parameters for susie
 * [Using UKbiobank data (chr17:22), fusion weights Adipose, test prior's effect for susie](simulation-multi-ukbchr17to22-gtex.adipose_susieprior.html)
    * [Visualization](https://users.rcc.uchicago.edu/~simingz/simulation-susieP-ukbchr17to22-gtex.adipose.html)

@@

## mr.ash + SUSIE iterative
*  [Using UKbiobank data (chr17:22), fusion weights Adipose](simulation-susieI-ukbchr17to22-gtex.adipose.html)

>>>>

@@

## mr.ash + SUSIE iterative
*  [Using UKbiobank data (chr17:22), fusion weights Adipose](simulation-susieI-ukbchr17to22-gtex.adipose.html) 
  *  [Using UKbiobank data (chr17:22), fusion weights Adipose, test prior's effect for susie](simulation-multi-ukbchr17to22-gtex.adipose_susieprior.html)

### 2020-09-14 analysis/simulation-multi-ukbchr17to22-gtex.adipose_susieprior.Rmd
susieI plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  message= F, warning = F)
```
`

@@

@@

# Setting 1

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/"
```

@@

## Using uniform prior:

```{r cali 0, fig.height=6, fig.width=6}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior1.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
```

## Use overestimated prior

* The prior used is: 
```{r  par1}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1, fig.height=6, fig.width=14}
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Use priors close to truth

```{r cali 2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Use under estimated priors

* The prior used is: 
```{r  par3}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_3.txt"), header = T)
t(par[c(1,3),1, drop = F])
```

* susie results: 
```{r cali 3, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior3.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

# Setting 2

We run 100 simulations and run susie using different priors and `L= 1`. We apply susie for all regions.

@@

* The true parameters we used to simulate data: 
```{r  true par all}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[,2, drop = F])
```

## Using uniform prior:

```{r cali 0 all, fig.height=6, fig.width=6}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior1.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
```

## Use overestimated prior

* The prior used is: 
```{r  par1 all}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1 all, fig.height=6, fig.width=14}
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Use priors close to truth

* The prior used is: 
```{r  par2 all}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```

```{r cali 2 all, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Use under estimated priors

* The prior used is: 
```{r  par3 all}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_3.txt"), header = T)
t(par[c(1,3),1, drop = F])
```

* susie results: 
```{r cali 3 all, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior3.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  message= F, warning = F)
```

@@

* For each simulation scenarios(1-x, 3-x), we picked two few parameter sets (priors for gene and snps) estimated by susieI and check if PIPs for genes are calibrated.

@@

# Simulation 1-x, setting 1
- filter criteria: rpip 0.3 and causal

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/20200721-1-fixprior_rpip0.3_causal/"
```

We run 100 simulations and run susie using different priors and `L= 1`. We only apply susie for regions with mr.ash2 regional PIP > 0.5.

## Use prior from susie estimates 1.

* The prior used is: 
```{r  par1}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Use prior from susie estimates 2.

```{r cali 2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

# simulation 1-x, setting 2
- filter criteria: rpip 0.3

```{r output a dir}
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/20200721-1-fixprior_rpip0.3/"
```

@@

* The true parameters we used to simulate data: 
```{r  true a par}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[,2, drop = F])
```

## Use prior from susie estimates 1.

* The prior used is: 
```{r  par1 a}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1 a, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Use prior from susie estimates 2.

* The prior used is: 
```{r  par2 a}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```

```{r cali 2 a, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

# Simulation 3-x, setting 1
- filter criteria: rpip 0.3 and causal

```{r output 3.1 dir}
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/20200721-3-fixprior_rpip0.3_causal/"
```

We run 100 simulations and run susie using different priors and `L= 1`. We only apply susie for regions with mr.ash2 regional PIP > 0.5.

@@

* The true parameters we used to simulate data: 
```{r  true par 3.1}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[,2, drop = F])
```

## Use prior from susie estimates 1.

* The prior used is: 
```{r  par1-2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Use prior from susie estimates 2.

* The prior used is: 
```{r  par2-2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 2-2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

# Simulation 3-x, setting 2
- filter criteria: rpip 0.3

```{r output dir 3.2}
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/20200721-3-fixprior_rpip0.3/"
```

We run 100 simulations and run susie using different priors and `L= 1`. We only apply susie for regions with mr.ash2 regional PIP > 0.5.

* The true parameters we used to simulate data: 
```{r  true par3.2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[,2, drop = F])
```

## Use prior from susie estimates 1.

* The prior used is: 
```{r  par3.2.1}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 3.2.1, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Use prior from susie estimates 2.

* The prior used is: 
```{r  par 3.2.2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 3.2.2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```
